---
title: "Tutorials on RNA-Seq Data Analysis"
author:
- name: Nicolas Delhomme
  affiliation: BN Bioinformatics Handelsbolag
  email: nicolas.delhomme.fleig@gmail.com
package: RnaSeqTutorials
output:
  BiocStyle::html_document
abstract: |
  There are six tutorials in this package to learn about data science in R, perform an 
  RNA-Seq Exploratory Data Analysis, a Differential Gene Expression analysis, a 
  Differential Transcript Usage analysis, a Gene Set Enrichment Analysis and an
  ensemble approach thereof.
  
vignette: |
  %\VignetteIndexEntry{RnaSeqTutorials}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Getting started

There are six tutorials:

1. 01_data_science_intro: an introduction to data science using the `palmerpenguins` package
2. 02_exploratory_data_analysis: the exploratory data analysis of a public RNA-Seq dataset
3. 03_differential_gene_expression: the differential expression DE analysis of the same dataset
4. 04_gene_set_enrichment_analysis: gene set enrichment analysis (GSEA) on the DE gene sets
5. 05_ensemble_gene_set_enrichment_analysis: ensemble GSEA of the DE gene sets and comparison to GSEA
6. 06_differential_transcript_usage: the differential transcript usage analysis of the same dataset

To start a tutorial run _e.g._:
```{r tutorial, eval=FALSE}
learnr::run_tutorial("01_data_science_intro", package = "RnaSeqTutorials")
```

# Accessing the code
## Tutorials
The tutorials are available as `.Rmd` files in the `tutorials` directory:
```{r tutorial list}
dir(system.file(package="RnaSeqTutorials","tutorials"))
```

```{r tutorial paths}
list.files(path=system.file(package="RnaSeqTutorials","tutorials"),
           pattern="*.Rmd",
           recursive=TRUE)
```

## Scripts
There are a number of scripts available in the `script` directory:
```{r script paths}
list.files(path=system.file(package="RnaSeqTutorials","scripts"),
           pattern="*.R",
           recursive=TRUE)
```

# Session info {.unnumbered}

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
